---
title: 'Grad2)'
author: "Anne-Kathrin Kleine"
date: "2/27/2020"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 1
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '1'
---
   
# Preselection 

```{r loading_packs, eval = T, include = F, echo = F}
knitr::opts_chunk$set(include = T, echo = T, warning = F, message = F)
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

packages <- c("mediation", "foreign", "tidyverse","stargazer","multicon", "ggplot2", "plyr", "reshape2", "readxl", 
              "scales", "grid", "tidyLPA", "Rcpp", "naniar", "dplyr", "car", "mice", 
              "rstudioapi", "labelled", "modi", "semPlot", "kulife")
ipak(packages)
```

```{r}
 #library(rstudioapi)
# set_wd <- function() {
# current_path <- getActiveDocumentContext()$path 
#  setwd(dirname(current_path ))
#  print( getwd() )
 # }
# set_wd()
```

```{r}

options(knitr.table.format = function() {
  if (knitr::is_latex_output()) 'latex' else 'pandoc'
})

library(rlang)
library(tidyverse)
library(foreign)
files <- dir(getwd(), pattern = "\\.sav$", full.names = FALSE) 
df_list <- vector("list", length(files))
names(df_list) <- files
read_in <- function(df = files) {
  for (fname in df) {
    df_list[[fname]] <- haven::read_sav(fname, encoding = NULL, user_na = FALSE, col_select = NULL,skip = 0, n_max = Inf, .name_repair = "unique") 
  }
    names(df_list) <- gsub(".sav","",names(df_list))
    ff <- df_list
}


df_list <- read_in(files)

list2env(df_list,envir=.GlobalEnv)

pre_df <- as.data.frame(Grad2_Preselection) %>% 
  dplyr::rename(
    DurationT1 = Duration__in_seconds_
    )

```

```{r}
# filter out all those with status != 0
pre_df <- pre_df[!(pre_df$Status!=0),]
pre_df <- pre_df[!is.na(pre_df$Status),]

# select random sample based on language distribution 
no_english_df <- pre_df$P_lang == 2 # find row numbers where lang == 2
perc.10<- round(sum(no_english_df, na.rm = T) * 0.1) # cut sample by 10%
no_english <- which(no_english_df == TRUE)
sampled.10 <- sample(no_english, perc.10) 
pre_df_sel <- pre_df[-sampled.10, ] # in your final output, include all but the 10%

nrow(pre_df)
nrow(pre_df_sel)

# filter out those who do not graduate this year 
pre_df_sel <- pre_df_sel[!(pre_df_sel$P_gradyear_1.0!=1),]
# filter out those who indicate <60% likelihood of graduating this year 
pre_df_sel <- pre_df_sel[!(pre_df_sel$P_anti_1 <= 60),]

```

## Sample sizes

### Full sample
```{r}
nrow(pre_df)
```

### those graduating in 2020
```{r}
nrow(pre_df_sel)
```


## Effects of coronacrisis on job prospects {.tabset}

### Full sample 

```{r include = T}
mean(pre_df$P_jobcorona_1, na.rm = T)
hist(pre_df$P_jobcorona_1, main = "Effects of coronacrisis on job prospects", xlab = "Magnitude", ylab = "Count", breaks = "Sturges")
```

### Selected sample (graduating in 2020)

```{r include = T}
mean(pre_df_sel$P_jobcorona_1, na.rm = T)
hist(pre_df_sel$P_jobcorona_1, main = "Effects of coronacrisis on job prospects", xlab = "Magnitude", ylab = "Count", breaks = "Sturges")
```

## Graduation date - delay due to corona crisis {.tabset}

### Full sample 

```{r include = T}
pre_df$P_gradyear_diff <- (pre_df$P_gradyear_1.0 - pre_df$P_gradyear_1)
pre_df$P_gradmonth_diff <- (pre_df$P_gradmonth_1.0 - pre_df$P_gradmonth_1)

pre_df$P_gradyear_diff <- pre_df$P_gradyear_diff*12
pre_df$P_grad_diff <- pre_df$P_gradyear_diff + pre_df$P_gradmonth_diff

mean(pre_df$P_grad_diff, na.rm = T)
barplot(table(pre_df$P_grad_diff),
        main = "Graduation date delay due to coronavirus crisis", 
        xlab = "Delay in months", 
        ylab = "Count",
        col = "blue",
        density = 30)
```

### Selected sample (graduating in 2020)

```{r include = T}
pre_df_sel$P_gradyear_diff <- (pre_df_sel$P_gradyear_1.0 - pre_df_sel$P_gradyear_1)
pre_df_sel$P_gradmonth_diff <- (pre_df_sel$P_gradmonth_1.0 - pre_df_sel$P_gradmonth_1)

pre_df_sel$P_gradyear_diff <- pre_df_sel$P_gradyear_diff*12
pre_df_sel$P_grad_diff <- pre_df_sel$P_gradyear_diff + pre_df_sel$P_gradmonth_diff

mean(pre_df_sel$P_grad_diff, na.rm = T)

barplot(table(pre_df_sel$P_grad_diff),
        main = "Graduation date delay due to coronavirus crisis", 
        xlab = "Delay in months", 
        ylab = "Count",
        col = "blue",
        density = 30)
```

## Anticipations (Selected sample)

```{r include = T}
mean(pre_df_sel$P_anti_1, na.rm = T)
hist(pre_df_sel$P_anti_1, main = "Likelihood of graduationg from university", xlab = "Likelihood", ylab = "Count", breaks = "Sturges")
```

```{r include = T}
mean(pre_df_sel$P_anti_2, na.rm = T)
hist(pre_df_sel$P_anti_2, main = "Likelihood of starting full-time employment", xlab = "Likelihood", ylab = "Count", breaks = "Sturges")
```

```{r include = T}
mean(pre_df_sel$P_anti_3, na.rm = T)
hist(pre_df_sel$P_anti_3, main = "Likelihood of starting part-time employment", xlab = "Likelihood", ylab = "Count", breaks = "Sturges")
```

```{r include = T}
mean(pre_df_sel$P_anti_4, na.rm = T)
hist(pre_df_sel$P_anti_4, main = "Likelihood of starting to work self-employed", xlab = "Likelihood", ylab = "Count", breaks = "Sturges")
```

```{r include = T}
mean(pre_df_sel$P_anti_5, na.rm = T)
hist(pre_df_sel$P_anti_5, main = "Likelihood of starting an internship", xlab = "Likelihood", ylab = "Count", breaks = "Sturges")
```

```{r include = T}
mean(pre_df_sel$P_anti_6, na.rm = T)
hist(pre_df_sel$P_anti_6, main = "Likelihood of becoming unemployed", xlab = "Likelihood", ylab = "Count", breaks = "Sturges")
```

```{r include = T}
mean(pre_df_sel$P_anti_7, na.rm = T)
hist(pre_df_sel$P_anti_7, main = "Likelihood of starting a new study", xlab = "Likelihood", ylab = "Count", breaks = "Sturges")
```

## Demographic information (Selected sample) {.tabset}

### Gender

```{r include = T}
library(plotly)
table(pre_df_sel$P_gender, useNA="always")
lbls <- c("Male", "Female", "Other", "NA")

count_df <- count(pre_df_sel, vars = "P_gender", wt_var = NULL) %>%
  .[2] %>% unlist(.) 


df_pie <- as_tibble(cbind(count_df, lbls))

fig <- plot_ly(df_pie, labels = ~lbls, values = ~count_df, type = 'pie')
fig_pie <- fig %>% layout(title = 'Gender',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
fig_pie
```

### Age 

```{r include = T}
pre_df_sel$P_age <- as.numeric(pre_df_sel$P_age)
# make all above 80 NA
pre_df_sel$P_age[pre_df_sel$P_age > 80] = NA

mean(pre_df_sel$P_age, na.rm = T)

hist(pre_df_sel$P_age, main = "Age", xlab = "Age", ylab = "Count", breaks = "Sturges")
```

### Native language English or other 

```{r include = T}
library(plotly)
table(pre_df_sel$P_lang, useNA="always")
lbls <- c("English", "Other", "NA")

count_df <- count(pre_df_sel, vars = "P_lang", wt_var = NULL) %>%
  .[2] %>% unlist(.) 


df_pie <- as_tibble(cbind(count_df, lbls))

fig <- plot_ly(df_pie, labels = ~lbls, values = ~count_df, type = 'pie')
fig_pie <- fig %>% layout(title = 'Native language',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
fig_pie

```

## Export white list 
```{r}
nrow(pre_df_sel)

pre_df_sel <- pre_df_sel[!duplicated(pre_df_sel$P_ID), ]

PID <- pre_df_sel %>% dplyr::select(matches("P_ID"))

write.csv(PID, "whitelist_p.csv", row.names=FALSE)
```

# T1 sample selection 

```{r}
files <- dir(getwd(), pattern = "\\.sav$", full.names = FALSE) 
df_list <- vector("list", length(files))
names(df_list) <- files
read_in <- function(df = files) {
  for (fname in df) {
    df_list[[fname]] <- haven::read_sav(fname, encoding = NULL, user_na = FALSE, col_select = NULL,skip = 0, n_max = Inf, .name_repair = "unique") 
  }
    names(df_list) <- gsub(".sav","",names(df_list))
    ff <- df_list
}


df_list <- read_in(files)

list2env(df_list,envir=.GlobalEnv)

pre_df <- as.data.frame(Grad2_Preselection) %>% 
  dplyr::rename(
    DurationT1 = Duration__in_seconds_
    )

T1 <- as.data.frame(Grad2_T1) %>% 
  dplyr::rename(
    DurationT1 = Duration__in_seconds_
    )

T1_2 <- as.data.frame(Grad2_T1_2) %>% 
  dplyr::rename(
    DurationT1 = Duration__in_seconds_
    )

T1_df <- rbind(T1, T1_2)

```

## Export white list 

```{r}
nrow(T1_df)

T1_sel <- T1_df[!duplicated(T1_df$t1id), ]

T1_PID <- T1_sel %>% dplyr::select(matches("t1id")) 
T1_PID <- T1_PID[grep("5", T1_PID$t1id), ]
T1_PID <- T1_PID[-c(1:2)]

write.csv(T1_PID, "whitelist_t1.csv", row.names=FALSE)
```

